\bf Properties and Bayesian fitting of restricted Boltzmann machines

### 2017-12-06 writing/paper-rbm/chapters/rbm.Rmd
submission 2
fix blinded

In other words, S-unstable RBM model sequences are guaranteed to stack up all probability on a specific set of outcomes for visibles, which could potentially be arbitrarily narrow. Proofs of Propositions \@ref(prp:instab1) and \@ref(prp:degen) appear in @kaplan2016propriety. These findings also have counterparts in results in @schweinberger2011instability, but unlike results there, we do not limit consideration to exponential family forms with a fixed number of parameters.

>>>>

In other words, S-unstable RBM model sequences are guaranteed to stack up all probability on a specific set of outcomes for visibles, which could potentially be arbitrarily narrow. Proofs of Propositions \@ref(prp:instab1) and \@ref(prp:degen) follow from more general results in @kaplan2016propriety. These findings also have counterparts in results in @schweinberger2011instability, but unlike results there, are not limited in consideration to exponential family forms with a fixed number of parameters.

### 2017-12-06 writing/paper-rbm/docs/paper.tex
fix blinded

In other words, S-unstable RBM model sequences are guaranteed to stack
up all probability on a specific set of outcomes for visibles, which
could potentially be arbitrarily narrow. Proofs of Propositions
\ref{prp:instab1} and \ref{prp:degen} follow from more general results
in Kaplan, Nordman, and Vardeman
(\protect\hyperlink{ref-kaplan2016propriety}{2016}). These findings also
have counterparts in results in Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), but unlike
results there, we do not limit consideration to exponential family forms
with a fixed number of parameters.

@@

\leavevmode\hypertarget{ref-kaplan2016propriety}{}%
Kaplan, Andee, Daniel Nordman, and Stephen Vardeman. 2016. ``On the
Propriety of Restricted Boltzmann Machines.'' \emph{arXiv Preprint
arXiv:1612.01158}.

>>>>

In other words, S-unstable RBM model sequences are guaranteed to stack
up all probability on a specific set of outcomes for visibles, which
could potentially be arbitrarily narrow. Proofs of Propositions
\ref{prp:instab1} and \ref{prp:degen} follow from more general results
in Kaplan, Nordman, and Vardeman
(\protect\hyperlink{ref-kaplan2016propriety}{2017}). These findings also
have counterparts in results in Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), but unlike
results there, are not limited in consideration to exponential family
forms with a fixed number of parameters.

@@

\leavevmode\hypertarget{ref-kaplan2016propriety}{}%
Kaplan, Andee, Daniel Nordman, and Stephen Vardeman. 2017. ``On the
Propriety of Restricted Boltzmann Machines.'' \emph{Unpublished}.

### 2017-12-06 writing/paper-rbm/docs/paper_blinded.tex
fix blinded

In other words, S-unstable RBM model sequences are guaranteed to stack
up all probability on a specific set of outcomes for visibles, which
could potentially be arbitrarily narrow. Proofs of Propositions
\ref{prp:instab1} and \ref{prp:degen} follow from more general results
in XXX (\protect\hyperlink{ref-kaplan2016propriety}{2016}). These
findings also have counterparts in results in Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), but unlike
results there, we do not limit consideration to exponential family forms
with a fixed number of parameters.

@@

@@

\leavevmode\hypertarget{ref-kaplan2016propriety}{}%
XXX, XXX. 2016. ``On the Propriety of Restricted Boltzmann Machines.''

>>>>

In other words, S-unstable RBM model sequences are guaranteed to stack
up all probability on a specific set of outcomes for visibles, which
could potentially be arbitrarily narrow. Proofs of Propositions
\ref{prp:instab1} and \ref{prp:degen} follow from more general results
in Kaplan, Nordman, and Vardeman
(\protect\hyperlink{ref-kaplan2016propriety}{2017}). These findings also
have counterparts in results in Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), but unlike
results there, are not limited in consideration to exponential family
forms with a fixed number of parameters.

@@

\leavevmode\hypertarget{ref-kaplan2016propriety}{}%
Kaplan, Andee, Daniel Nordman, and Stephen Vardeman. 2017. ``On the
Propriety of Restricted Boltzmann Machines.'' \emph{Unpublished}.

@@
